\subsection{Data persistance with Mnesia}\label{subsec:archmnesia}

The persistence of data (auctions and bids) is managed by Mnesia, a distributed
telecommunications DBMS that allows persistence, data replication, atomic
transactions, and location transparency.

For the persistence of auctions and bids, two tables of type \textit{set} have
been created on Mnesia. To define the attributes of the tables, the following
records been defined.

\begin{lstlisting}[language=Erlang, caption=Mnesia Record]
    -record(auction,{
        id_auction,
        id_agent,
        name,
        image,
        description,
        end_date,
        min_price,
        min_raise,
        sale_quantity
    }).

    -record(bid, {
        id_bid,
        id_auction,
        id_user,
        timestamp,
        bid_value,
        quantity
    }).
\end{lstlisting}

Through a specific Erlang module the following methods have been defined to
interact with Mnesia. All the operations inside the methods have been
implemented through \code{mnesia:transaction} which allows to perform
transactional operations on Mnesia.

\begin{description}
	\item[insert\_auction] insert the auction passed as value.
	\item[insert\_bid] insert the bid passed as value.
	\item[delete\_auction] delete the auction with the id passed as value.
	\item[delete\_bid] delete the bid with the id passed as value.
	\item[get\_auction] returns a specific auction.
	\item[get\_bid\_list] returns the list of bids for an auction (and
		optionally, of a given user).
	\item[get\_auction\_list] returns the list of auctions available.
	\item[get\_bidder\_auctions] returns the list of auctions in which the
		user has made at least 1 bid.
	\item[get\_agent\_auctions] returns the list of auctions created by an
		agent.
\end{description}
