\chapter{Specifications}\label{ch:specs}

The application developed for this workgroup task is a tool for \standout{online
auctions}.

The main purpose of the application is to allow people to put items up for sale
through auctions and allow people to try to buy items by bidding in available
auctions.

An \textbf{auction} sells a number of items with a fixed minimum price for each
item. Each \textbf{bid} defines the number of items you want to buy, and the
price offered for each item. The auction system, for each bid made or deleted,
will have to calculate the list of winning bids that maximize profit,
considering as parameters the number of items for sale and the timestamp of the
bids. The auction system of this application is set to \underline{``all or
nothing'' semantics}, this means that winning bids will get the required
quantity of items. If there are not enough items, the bid will not be placed
among the winning ones.

Before login, a user must register to the application specifying its username
and password. When logged in, the user can see the list of the available
auctions. A user can select an auction from the list and view all the
information of that auction and, if he wishes, can place a bid. Once a bid has
been made, the user can follow the progress of the auction in real time in this
page (if his bid is among the winning ones) and the auction will be added to the
list of followed auctions which you can view later in a special section. Also,
if you are no longer interested, the user can delete the bid.

A user can see the list of auctions created in a special section and can select
a specific auction to see its progress in real time or its result.
